Supporting Information

### 2018-03-13 SupportingInformation.Rmd
fixing typo

<!--
```{r, echo=F}
options(knitr.table.format = "html")

```
-->

@@

We also defined a statistic $\Ps_{l_b,u_b}$, using the same bounds
$u+v=2l_b$ and $u+v=2u_b$, as follows. For a distance $h$, we defined
$S(h)$ to be the number of points $(u_i,v_i)$ within the bounds 
and a distance less than $h$ from the line $v=u$, divided by the 
total number of points within the bounds. This function is
defined for $h$ going from $0$ to a distance $h_{\text{max}}$ which
is half the longer of the two segments obtained by intersecting the
bounds with the unit square. It is easy to see $S(0)=0$ and 
$S(h_{\text{max}})=1$. We defined $S_i(h)$, for the same range 
of $h$, to be the area within the bounds and the unit square
and within distance $h$ of the line $v=u$, divided by the area
within the bounds and the unit square. This is the expected value of
$S(h)$ for independent data. We then defined
\begin{equation}\label{eq.P}
   P_{l_b,u_b} = \int_0^{h_{max}} ( S(h) - S_i(h) ) dh.
\end{equation}
As for $\cor_{l_b,u_b}$, larger values of $Ps_{l_b,u_b}$ 
indicate stronger positive association
between $u$ and $v$ in the region given by the bounds.

>>>>

<!--
```{r, echo=F}
options(knitr.table.format = "html")
```
-->

@@

We also defined a statistic $\Ps_{l_b,u_b}$, using the same bounds
$u+v=2l_b$ and $u+v=2u_b$, as follows. For a distance $h$, we defined
$S(h)$ to be the number of points $(u_i,v_i)$ within the bounds 
and a distance less than $h$ from the line $v=u$, divided by the 
total number of points within the bounds. This function is
defined for $h$ going from $0$ to a distance $h_{\text{max}}$ which
is half the longer of the two segments obtained by intersecting the
bounds with the unit square. It is easy to see $S(0)=0$ and 
$S(h_{\text{max}})=1$. We defined $S_i(h)$, for the same range 
of $h$, to be the area within the bounds and the unit square
and within distance $h$ of the line $v=u$, divided by the area
within the bounds and the unit square. This is the expected value of
$S(h)$ for independent data. We then defined
\begin{equation}\label{eq.P}
   P_{l_b,u_b} = \int_0^{h_{max}} ( S(h) - S_i(h) ) dh.
\end{equation}
As for $\cor_{l_b,u_b}$, larger values of $\Ps_{l_b,u_b}$ 
indicate stronger positive association
between $u$ and $v$ in the region given by the bounds.
